Goals and Tasks

### 2020-05-04 TO_DO.Rmd
new tasks clipped

---
title: 'Goals and Tasks'
author: "ASP Boost Team"
date: "30 4 2020"
output: html_document
---

@@

I propose this file for technical discussion and goal setting and tracking. 
Goal setting could look like this (This is merely a sketch):

## Tasks to achieve till next Q&A session 20.05.04 
### (as set in the last meeting)

* ~~README~~ L. 
* ~~Rmd file for communication~~ S (this file)
* Push a boost function JLS.

Initials could indicate whom belongs which task.

>>>>

---
title: 'Goals and Tasks'
author: "ASP Boost Team"
date: "30 April 2020"
output: html_document
---

@@

This file is for goal setting and tracking and technical discussion.

## Tasks until ~ 11 May

* simple boost function for scale (estimate var(yi))
* read Wickham "R-Packages"
* try implementing function-testing
* get used to roxygen2

## Tasks to achieve till next Q&A session 04 May 2020 
### (as set in the last meeting)

* L ~~README~~ . 
* S ~~Rmd file for communication~~  (this file)
* JLS ~~Push a boost function~~

Initials indicate whom belongs which task.
